SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-12-08 build/submit_v1/maintex.tex
added build folder

%%%Integral Field Spectroscopy%%%
The previously mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 2\arcsec\ diameter optical fibers. With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can now be studied with unprecedented spatial detail. These surveys allow us to study the centers of merging galaxies more rigorously since apertures can be set to the physical scale of the galaxies instead of being bound by a fixed sky aperture. These IFS surveys will also allow us to see the extent of the centrally induced star formation and to see how the star formation in the disks of the galaxies are affected.

@@

We then take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space). This gives us the difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}). Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.35$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff. In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex. All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile. For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is significantly higher than the median profile (reaching 0.5$-$0.6 dex). As will be discussed in \S~\ref{sec:tailored}, we believe this elevated enhancement in the highest mass bin is driven by more compact mergers instead of stellar mass.

@@

Figure \ref{fig:ssfr_sep} shows the profile and the central level of sSFR enhancement as a function of the projected separation ($r_{\rm p}$) from our MaNGA data. The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations. The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.05$-$0.1 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.

>>>>

%%%Integral Field Spectroscopy%%%
The previously mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 1-1.5\arcsec-radius optical fibers. With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can now be studied with unprecedented spatial detail. These surveys allow us to study the centers of merging galaxies more rigorously since apertures can be set to the physical scale of the galaxies instead of being bound by a fixed sky aperture. These IFS surveys will also allow us to see the extent of the centrally induced star formation and to see how the star formation in the disks of the galaxies are affected.

@@

We then take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space). This gives us the difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}). Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.3$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff. In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex. All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile. For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is significantly higher than the median profile (reaching 0.5$-$0.6 dex). As will be discussed in \S~\ref{sec:tailored}, we believe this elevated enhancement in the highest mass bin is driven by more compact mergers instead of stellar mass.

@@

Figure \ref{fig:ssfr_sep} shows the profile and the central level of sSFR enhancement as a function of the projected separation ($r_{\rm p}$) from our MaNGA data. The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations. The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.1$-$0.15 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.
